### 2016-07-13 Projects/DelCo_2012/Report/DelCo_2012.tex
change font on fire suppression timing, start appendix cafs

>>>>

\begin{figure}[ht]
\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A1}
\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top, middle) and in the Hallway (bottom) for Single-Story Fire Suppression Test CAF~1}
\end{figure}
